\Large{All in the family:\\German twin finishing times in\\the 2016 women's Olympic marathon}

### 2017-02-17 paper/chance_memo.tex
ref memo start
memo update

@@

\item ``5a'' and ``5b''

>>>>

\item ``Marathon finish may be linearly related to the fastest
  previous marathon with perhaps age in a model. An interesting though
  experiment may be, if they were blindfolded, would they have
  finished together?''

@@

\item There are errors in figure labels, ``5a'' and ``5b''

  We apologize for this oversight and have fixed the associated
  labeling errors.
